Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

For testing purposes, 3 significant or alpha levels will be used
different, namely 0.1, 0.05, and 0.001. These three significant levels are used for
knowing the sensitivity of the regression detection results with the meaning that the smaller the value of
significant, the more significant the evidence to reject h0. Significant value 0.1
was chosen as the upper limit of the significant value to determine the sensitivity level of
test case with the greatest significant value. While the value of 0.05 was chosen because
this value is the most commonly used value as a significant value
on the statistical test of the hypothesis. While the value of 0.001 was chosen as a comparison of the value of
least significant to test the lower limit of the significant value.

>>>>

For testing purposes, 3 significant levels or alpha will be used, those are 0.1, 0.05, and 0.001. These three significant levels are used for knowing the sensitivity of the regression detection results with interpretation that the smaller the value of
significant levels, the more significant the evidence to reject $h_{0}$. Significant value 0.1
was chosen as the upper limit of the significant value to determine the sensitivity level of test case with the greatest significant value. While the value of 0.05 was chosen because this value is the most commonly used value as a significant value on the statistical test of the hypothesis. While the value of 0.001 was chosen as a comparison of the value of least significant to test the lower limit of the significant value.
